\section{Qualitative System Analysis}

This section provides a qualitative treatment of the reaction of the Havven system in response to various scenarios listed below:

% \todo[inline]{Scenario analysis.}

\subsection{Incentives}

\paragraph{Why would anyone use nomins?}
\begin{itemize}
	\item Versus havvens?
	\item Versus alternatives?
\end{itemize}

\paragraph{Why would anyone issue nomins?}
\begin{itemize}
	\item Fees
	\item Because they thought the peg would break in the positive direction.
\end{itemize}

\subsection{Scenarios}

\subsubsection{Havvens appreciate against nomins.} \label{sec:havven-nomin-appreciation}
\begin{itemize}
	\item{Havven-holders can issue more nomins.}

	This might be scary because we either want the nomin supply to fall, or nomin demand to increase.
	This is fine if the nomin price fell, because then nomin demand should increase.
	However, if it was simply that the havven price increased, then this might encourage
	oversupply of nomins as issuers compete for shares of the fee pool.

	\item{Cheaper exit}

	Anyone who has previously issued havvens but who wants to exit can buy nomins for
	cheaper than they issued them at, so egress with a profit.
	Alternatively, if the havven price doubles, then only half of their stake is required
	to back the nomins they have issued. They can use these proceeds to completely liquidate
	their position.

	\item{Each nomin locks fewer havvens.}
	
\end{itemize}

\subsubsection{Havvens depreciate against nomins.} \label{sec:havven-nomin-depreciation}

\begin{itemize}
	\item{Havven-holders can issue fewer nomins.}
	
	Perhaps they may even be under-staked.

	\item{Each nomin locks more havvens.}
	\item{A player can issue a quantity of nomins and sell them for havvens.}
		  
	They would do this on the assumption that, once the nomin price decreases as a result of the increased
	supply, they will be able to buy back the same quantity of nomins to free up their
	havvens more cheaply.
\end{itemize}

\subsubsection{Nomin/havven liquidity dries up}
\begin{itemize}
	\item Low nomin supply

	Nomins should appreciate against the havven. See \cref{sec:havven-nomin-depreciation}.
	Fee takings will decrease, hurting havven-holders in the long run,
	which should incentivise them to inject nomins into the ecosystem.

	\item Low havven supply

	If system backers are sitting on a pile of havvens, then the havven should
	appreciate. See \cref{sec:havven-nomin-appreciation,sec:havven-appreciation}.
\end{itemize}


\subsubsection{Long-run havven price appreciation}\label{sec:havven-appreciation}
% \todo[inline]{Long-run havven appreciation scenario.}
In this instance, over the long run, the price of havvens could appreciate quite substantially,
which will lead to an increase in nomin issuance rights (and so probably actual nomins in circulation).
There are at least two reasons that havvens could appreciate:
\begin{itemize}
	\item Increased nomin velocity/demand, leading to greater fees;
	This is fine: in this case, nomin issuance rights increase in proportion with demand for the currency.

	\item Speculation
	This is not so fine: in this case, the nomin supply can be expanded without any accompanying
	expansion in its demand, which will depress the nomin price.
	% \todo[inline]{Resolve disconnect between speculation-driven value of havvens and nomin supply.}
\end{itemize}

\subsubsection{Long-run havven price depreciation}\label{sec:havven-depreciation}
% \todo[inline]{Long-run havven depreciation scenario.}

\subsubsection{Radical shifts in usage}
% \todo[inline]{Usage-shift scenario.}

% \todo[inline]{List expected players in the market.}
% \todo[inline]{Outline incentives and actions for different players.}


\subsection{Expected Market Players}

\begin{itemize}
	\item{Havven Holders}

	A havven-holder provides the collateral and liquidity for the system. It is assumed that havven holders seek fee revenues,
	and escrow most of their havvens at any point in time. While this fee incentive holds if havvens are relatively stable in the long term, Havven also provide incentives for stabilising nomin price in in the short term. 

	\item{Nomin Users}

	Merchants, consumers, service providers, cryptocurrency market actors and so on: people who use the stable coin as a
	medium of exchange or as a means to hedge other forms of value. Nomin users provide a base demand for nomins, which is necessary for fees
	to exist. These users may be disincentivised from using the system in high fee situations or with excessive volatility
	in the price of nomins.

	\item{Arbitrageurs, Market Makers}

	The arbitrage force allows us to assume that the havven/nomin, havven/fiat, nomin/fiat
	prices are properly in alignment or will soon become aligned. Market-making activities
	allow us to neglect the bid/ask spread, and situations where there is insufficient
	liquidity for players to transact.
	
	\item{Speculators}
	
	Speculators may tend to magnify price corrections, and are a significant vector by which to introduce
	exogenous shocks to the system. In modelling this we induce volatility through simulating modes such as large capital flows in response to breaking news.
	
	%\item{Malicious Attackers}
	
	%We should examine what happens if a George Soros (or otherwise) attacks Havven.
	% \todo[inline]{List the various possible attacks against the system.}

	\item{Central Banker}
	
	While the system is designed to work without intervention, the Havven foundation will have capital reserves with which to intervene
	in the market to stabilise nomin prices in extreme situations.
	The advantage of such a market participant is, given that a very large market entity is
	willing to underwrite the stability of the coin, profit strategies predicated upon the
	stability of the token become less risky and so more feasible. The Havven foundation in
	this capacity takes on the role of providing confidence.

\end{itemize}



\pagebreak